### 2018-11-16 ms/ms_prosop.tex
finalized manuscript, added stimuli of faceAttract study

	\renewcommand{\familydefault}{\sfdefault}\normalfont
	\centering
	\includegraphics[width=\columnwidth]{../reports/figures/overview_heatmap_mod.png}
	\vspace*{-3mm}
 		\caption{\textbf{Comparison of JB's performance for all major tasks.} Differences in z-scores for all pairings of tasks are reported, with positive scores indicating higher performance for the tasks listed in the rows, compared to the tasks listed in the columns. Differences larger than two standard deviations are highlighted by stronger colors and an annotation indicating the numerical difference in z-scores. The emerging pattern suggests that JB’s performance is impaired for tasks involving learning of multiple faces (CFMT 2 and 3), and the recognition of famous faces from their inner parts, compared to learning of a single face (CFMT 1) and the recognition of emotion, intention (Eyes test) and attractiveness in faces. CFMT: Cambridge Face Memory Test; Eyes test: Reading the mind in the eyes; BRLT: Bergen Right-Left Discrimination Test; LPS2-Visual: Leistungsprüfsystem 2 (“performance test system”), test of visuo-spatial skills.}%
 		\label{fig:heat}

@@

\subsection*{Bergen Right-Left Discrimination Test}
Body perception and mental rotation of bodies were tested using the The Bergen Right-Left Discrimination Test (BRLD; \citet{Ofte_2002}). The test requires to identify the left and right hand on stick figures, which is made difficult by the figures shown from the front or back, and sometimes crossing their hands (BRLD-A). This is followed by a variation of the test where all stick figures are shown upside-down (BRLD-B) \citep{Grewe_2014}. A maximum score of 144 can be reached for each part. Normative values based on a sample of n=174 adult participants (124 female, mean age 28 years) was taken from \citet{Grewe_2014}. For the BRLD-A, the normative sample has a mean score of 110 and standard deviation of 25. For the BRLD-B, the normative sample has a mean score of 110 and standard deviation of 28.

@@

\subsection*{Reading the Mind in the Eyes Test}
In the test, participants see the eye region of a single face and have to select which of four terms best describes the mental state expressed by that face. A total score of 36 can be reached. To compute percentile scores, we used a normative sample of 50 female student controls from a previous study \citep{Baron_Cohen_2001}. This group has a mean score of 28.6 and standard deviation of 3.2.

\subsection*{Emotion expression task}
To test participants’ performance in recognizing facial expressions we used a 7-way forced-choice decision task with happy, sad, angry, fearful, disgusted, surprised and neutral faces. The face stimuli were taken from the NimStim database \citep{Tottenham_2009} and each emotion was displayed by a total of 12 different actors. In the experiment, a single face was shown for up to four seconds, and the participants were asked to chose which of the seven possible emotion expressions it depicts. The control sample consists of 17 males (mean age 43, range 24–58), hence controls are not matched regarding gender. The paradigm and the control group for this task are described in a previous publication \citep{Wegrzyn_2017}. The experiment was programmed and presented using PsychoPy2.

@@

\subsection*{Statistical Methods}
For each test, the percent of correct responses was computed as the ratio of JB’s score relative to the maximal achievable score. JB’s z-score for each test was computed based on the control sample’s distribution of scores, which was transformed to have zero mean and unit variance. The z-scores were converted into percentile scores using a cumulative distribution function. Inferential statistics were computed using the t-test method developed by Crawford \& Howell, as described in \citet{Crawford_2009}. Two-sided p-values were computed based on the t-value and the n-1 degrees of freedom (n being the size of the control sample). All computations were implemented using in-house software written in Python 2.7. A heatmap visualizing the differences of JB’s z-scores in all major tasks was created using Seaborn (seaborn.pydata.org).

@@

\subsubsection*{Ethics approval and consent to participate}
\small{All participants gave informed consent before taking part in the experiment, which was approved by the ethics board of Bielefeld University (ethics statement 2016-133).}

>>>>

	\renewcommand{\familydefault}{\sfdefault}\normalfont
	\centering
	\includegraphics[width=\columnwidth]{../reports/figures/overview_heatmap_mod.png}
	\vspace*{-3mm}
 		\caption{\textbf{Comparison of JB's performance for all major tasks.} Differences in z-scores for all pairings of tasks are reported, with positive scores indicating higher performance for the tasks listed in the rows, compared to the tasks listed in the columns. Differences larger than two standard deviations are highlighted by stronger colors, with the given annotations indicating the numerical difference in z-scores. The emerging pattern suggests that JB’s performance is impaired for tasks involving learning of multiple faces (CFMT 2 and 3), and the recognition of famous faces from their inner parts, compared to learning of a single face (CFMT 1) and the recognition of emotion, intention (Eyes test) and attractiveness in faces. CFMT: Cambridge Face Memory Test; Eyes test: Reading the mind in the eyes; BRLT: Bergen Right-Left Discrimination Test; LPS2-Visual: Leistungsprüfsystem 2 (“performance test system”, test of visuo-spatial skills).}%
 		\label{fig:heat}

@@

\subsection*{Bergen Right-Left Discrimination Test}
Body perception and mental rotation of bodies were tested using the The Bergen Right-Left Discrimination Test (BRLD; \citet{Ofte_2002}). The test requires to identify the left and right hand on stick figures, which is made difficult by presenting the figures from the front or the back, and sometimes presenting figures with their hands crossed (BRLD-A). This is followed by a variation of the test where all stick figures are shown upside-down (BRLD-B) \citep{Grewe_2014}. A maximum score of 144 can be reached for each part. Normative values based on a sample of n=174 adult participants (124 female, mean age 28 years) were taken from \citep{Grewe_2014}. For the BRLD-A, the normative sample has a mean score of 110 and standard deviation of 25. For the BRLD-B, the normative sample has a mean score of 110 and standard deviation of 28.

@@

\subsection*{Reading the Mind in the Eyes Test}
In the test, participants see the eye region of a single face and have to select one of four terms that best describes the mental state expressed by that face. A total score of 36 can be reached. To compute percentile scores, we used a normative sample of 50 female student controls from a previous study \citep{Baron_Cohen_2001}. This group has a mean score of 28.6 and standard deviation of 3.2.

\subsection*{Emotion expression task}
To test participants’ performance in recognizing facial expressions we used a 7-way forced-choice decision task with happy, sad, angry, fearful, disgusted, surprised and neutral faces. The face stimuli were taken from the NimStim database \citep{Tottenham_2009} and each emotion was displayed by a total of 12 different actors. In the experiment, a single face was shown for up to four seconds, and the participants were asked to choose which of the seven possible emotion expressions it depicts. The control sample consists of 17 males (mean age 43, range 24-58), hence controls are not matched regarding gender. The paradigm and the control group for this task are described in a previous publication \citep{Wegrzyn_2017}. The experiment was programmed and presented using PsychoPy2.

@@

\subsection*{Statistical Methods}
For each test, the percent of correct responses was computed as the ratio of JB’s score relative to the maximal achievable score. JB’s z-score for each test was computed based on the control sample’s distribution of scores, which was transformed to have zero mean and unit variance. The z-scores were converted into percentile scores using a cumulative distribution function. Inferential statistics were computed using the t-test method developed by Crawford and Howell, as described in \citet{Crawford_2009}. Two-sided p-values were computed based on the t-value and the n-1 degrees of freedom (n being the size of the control sample). All computations were implemented using in-house software written in Python 2.7. A heatmap visualizing the differences of JB’s z-scores in all major tasks was created using Seaborn (seaborn.pydata.org).

@@

\subsubsection*{Ethics approval and consent to participate}
\small{All participants gave informed consent before taking part in the study, which was approved by the ethics board of Bielefeld University (ethics statement 2016-133).}
